---
title: "Round 1, 2018"
description: "Super Netball Wrap-up"
date: "2018-05-02"
tags: ["r", "sports analytics"]
categories: ["blog", "Super Netball"]
---

<!-- Time-stamp: <2018-05-03 20:55:31 (slane)> -->

```{r setup,echo=FALSE,warning=FALSE,message=FALSE,cache=FALSE,results="hide"}
knitr::opts_chunk$set(cache = FALSE, error = FALSE, warning = FALSE,
                      message = FALSE, echo = FALSE, out.width = "900px",
                      out.height = "506px", dpi = 180, fig.align = "center",
                      fig.asp = 9/16)
options(digits = 2)

```

```{r libraries}
library(here)

```

The first round of the 2018 Super Netball season is complete, and what a cracker! I'm a Vixens fan, and it was a thriller --- hopefully they get stronger, and put the wins away, my ticker can't take much more than that! If you missed my round one predictions, [here they are]({{< relref "2018-04-25-round1.md" >}}).

## Wrap-up

```{r prediction-table}
preds <- readRDS(here("Rmd", "sn-assets", "round2-2018", "results_match.rds"))
knitr::kable(preds)

```

So how'd the model do? Well, the Vixens v.s. Magpies I think was spot on; definitely beginners luck!

The Thunderbirds were dead set favourites; given they were bottom-dwellers last year, this seems out of whack, but the Fever were only just above them in the ladder stakes. Add to this the fact the Thunderbirds had a reasonable predicted home game advantage ([see here]({{< relref "2018-04-22-introduction.md" >}})).

The Lightning was likewise firm favourites, given their winning form last season, but the Giants pipped them.

And another close one to close out the round. Firebirds were hot favourites in this one, even though they finished only one ladder position above the Swifts. In terms of team ability at the end of last season, they were well ahead though. The points go to the Swifts though!

So, overall, my model is not quite as well calibrated as one would hope. Let's see what happens for my [Round 2]({{< relref "2018-05-03-round2.md" >}}) predictions; I may need to tweak my model somewhat!
