---
title: "Preliminary Final, 2018"
description: "Super Netball Wrap-up"
date: "2018-08-21"
tags: ["r", "sports analytics"]
categories: ["blog", "Super Netball"]
---

<!-- Time-stamp: <2018-08-22 19:57:07 (slane)> -->

```{r setup,echo=FALSE,warning=FALSE,message=FALSE,cache=FALSE,results="hide"}
knitr::opts_chunk$set(cache = FALSE, error = FALSE, warning = FALSE,
                      message = FALSE, echo = FALSE, out.width = "900px",
                      out.height = "506px", dpi = 180, fig.align = "center",
                      fig.asp = 9/16)
options(digits = 2)

```

```{r libraries}
library(here)

```

An excellent game this week, and what stellar form the Lightning are in. I'm really looking forward to next week, it'll be a fantastic game. The Lightning are hot, but the Fever have had the week off. It's going to be hard for the Lightning to win in the West.

The model has got the goods done for this round. The most likely score difference was around six ([see the prediction here]({{< relref "2018-08-15-round16.md" >}})), and as we all know by now, it was the Lightning by nine.

## How did it all pan out?

```{r prediction-table}
preds <- readRDS(here("Rmd", "sn-assets", "round17-2018", "results_match.rds"))
knitr::kable(preds)

```
