---
title: "Round 2, 2018"
description: "Super Netball Wrap-up"
date: "2018-05-10"
tags: ["r", "sports analytics"]
categories: ["blog", "Super Netball"]
---

<!-- Time-stamp: <2018-05-11 17:32:43 (slane)> -->

```{r setup,echo=FALSE,warning=FALSE,message=FALSE,cache=FALSE,results="hide"}
knitr::opts_chunk$set(cache = FALSE, error = FALSE, warning = FALSE,
                      message = FALSE, echo = FALSE, out.width = "900px",
                      out.height = "506px", dpi = 180, fig.align = "center",
                      fig.asp = 9/16)
options(digits = 2)

```

```{r libraries}
library(here)

```

Another round bites the dust! What's happened to the Lightning and the Magpies? A slow start to the season, time will tell to see if they recover. If you missed my round 2 predictions, [here they are]({{< relref "2018-05-03-round2.md" >}}).

## Wrap-up

```{r prediction-table}
preds <- readRDS(here("Rmd", "sn-assets", "round3-2018", "results_match.rds"))
knitr::kable(preds)

```

A bit like [round 1]({{< relref "2018-05-02-round1-wrapup.md" >}}), round 2's predictions were a mixed bag. We started off with a bang, with the model suggesting that the Giants had a 90% chance of a win, which they did, and by good margin as well.

About a line ball for the Fever v.s. Magpies game, with the Magpies slightly favoured. Fever won strongly, and places them at the top of the table.

The Lightning were strongly predicted to beat the Firebirds (72%), but the Firebirds got the points with a 3 goal win.

The Vixens were favoured to beat the Swifts (75%), and did so, but not convincingly.

It looks like the model is still carrying a hangover from last season. It will be interesting to see how long it takes to revert to this season. We need to remember though, that the model only uses the score differential (and home ground advatange which is small) to make predictions; perhaps we can't expect too much from such a naive model.

Check out the round 3 predictions [here]({{< relref "2018-05-11-round3.md" >}}).
