---
title: "Round 1, 2019"
description: "Super Netball Wrap-up"
date: "2019-05-03"
tags: ["r", "sports analytics"]
categories: ["blog", "Super Netball"]
---

<!-- Time-stamp: <2019-05-04 14:56:51 (slane)> -->

```{r setup,echo=FALSE,warning=FALSE,message=FALSE,cache=FALSE,results="hide"}
knitr::opts_chunk$set(cache = FALSE, error = FALSE, warning = FALSE,
                      message = FALSE, echo = FALSE, out.width = "900px",
                      out.height = "506px", dpi = 180, fig.align = "center",
                      fig.asp = 9/16)
options(digits = 2)

```

```{r libraries}
library(here)

```

Well, I wish I could write something great about round 1, but I can't (apart from Go Vixens!). The model was hot on the Swifts, but gave 0 chance to the Magpies and Thunderbirds&emsp;the Thunderbirds are on the board! Clearly there's some model calibration that needs to happen. If you missed my round one predictions, [here they are]({{< relref "2019-04-27-round1.md" >}}).

## Wrap-up

```{r prediction-table}
preds <- readRDS(here("data/sn-assets-2019-round-2", "results_match.rds"))
knitr::kable(preds)

```

With some crazy stuff happening, I'm not doing a full write up for a while, but will endeavour to document the models and results at least. Let's see what happens for my [Round 2]({{< relref "2019-05-04-round2.md" >}}) predictions.
