---
title: "Round 3, 2019"
description: "Super Netball Wrap-up"
date: "2019-05-14"
tags: ["r", "sports analytics"]
categories: ["blog", "Super Netball"]
---

<!-- Time-stamp: <2019-05-07 16:39:41 (slane)> -->

```{r setup,echo=FALSE,warning=FALSE,message=FALSE,cache=FALSE,results="hide"}
knitr::opts_chunk$set(cache = FALSE, error = FALSE, warning = FALSE,
                      message = FALSE, echo = FALSE, out.width = "900px",
                      out.height = "506px", dpi = 180, fig.align = "center",
                      fig.asp = 9/16)
options(digits = 2)

```

```{r libraries}
library(here)

```

It's a bit of a lacklustre start to the year for the Firebirds. A draw at home,
following the loss in the first round sees them in the bottom half of the
ladder.

The model had the Lightning as slight favourites, yet they blew the Fever away
with a 25 point win. Model was bang on for the Swifts and Vixens, with large
wins by those two teams as well. Maybe we're heading towards the calibration
already?

If you missed my round three predictions, [here they are]({{< relref
"2019-05-07-round3.md" >}}).

## Wrap-up

```{r prediction-table}
preds <- readRDS(here("data/sn-assets-2019-round-4", "results_match.rds"))
knitr::kable(preds)

```

My [Round 4]({{< relref "2019-05-15-round4.md" >}}) predictions are in, so check
them out!
