---
title: "Semi Finals, 2018"
description: "Super Netball Wrap-up"
date: "2018-08-14"
tags: ["r", "sports analytics"]
categories: ["blog", "Super Netball"]
---

<!-- Time-stamp: <2018-08-15 20:35:18 (slane)> -->

```{r setup,echo=FALSE,warning=FALSE,message=FALSE,cache=FALSE,results="hide"}
knitr::opts_chunk$set(cache = FALSE, error = FALSE, warning = FALSE,
                      message = FALSE, echo = FALSE, out.width = "900px",
                      out.height = "506px", dpi = 180, fig.align = "center",
                      fig.asp = 9/16)
options(digits = 2)

```

```{r libraries}
library(here)

```

Wow! What a turn of events. With the Giants stellar form, I would have had them at an even stronger chance of winning than my model, yet the Fever triumphed---they get the week off, and it's straight through to the finals. Meanwhile, the Lightning pulled off an exciting one goal win over the Firebirds, given some sort of solace to us pouting Vixens fans, in that they keep on keeping on.

## Wrap-up

If you missed my semi final predictions, [here they are]({{< relref "2018-08-09-round15.md" >}}).

```{r prediction-table}
preds <- readRDS(here("Rmd", "sn-assets", "round16-2018", "results_match.rds"))
knitr::kable(preds)

```
