---
title: "Round 3, 2018"
subtitle: "Round 2 Wrapup and Round 3 Analysis"
---

<!-- Time-stamp: <2018-05-08 16:50:36 (slane)> -->

```{r setup,echo=FALSE,warning=FALSE,message=FALSE,cache=FALSE,results="hide"}
knitr::opts_chunk$set(cache = FALSE, error = FALSE, warning = FALSE,
                      message = FALSE, echo = TRUE, out.width = "900px",
                      out.height = "506px", dpi = 180, fig.align = "center",
                      fig.asp = 9/16, cache.path = "round2-2018_cache/")
options(digits = 2)

```

# Introduction

Going forward, these documents will wrap up the results from the previous round, and perform predictions for the next round.

The following packages are required:

```{r libraries}
library(dplyr)
library(tidyr)
library(purrr)
library(superNetballR)
library(rstan)
library(parallel)
library(here)
library(ggplot2)
library(cowplot)
library(forcats)
rstan::rstan_options(auto_write = TRUE)
cores <- round(parallel::detectCores() - 2)
options(mc.cores = cores)
source(here("R", "fit_funs.R"))
source(here("R", "ggsteve.R"))
source(here("R", "updateData.R"))
theme_set(theme_steve(base_size = 24))
if (!dir.exists(here("Rmd", "sn-assets", "round3-2018"))) {
    dir.create(here("Rmd", "sn-assets", "round3-2018"), recursive = TRUE)
}

```

## Round 2 Wrap-up

First, let's download the round 2 data, and update the seasonal data:

```{r round2-download}
season_2018 <- updateData(2)

```

Now, let's calculate the match results and running ladder:

```{r round2-results}
match_results <- matchResults(season_2018) %>%
    filter(round == 2)
ladder <- ladders(season_2018, 2)

```

Doh! The changes to the format means my ladder function is wrong now --- I need to calculate quarter winners as well. Leave that as a to do.

Need to write a function that takes match results, and transforms them into a table like the one I produce for predictions. Then I can compare the two.

```{r round2-games}
results <- matchPredictions(2, 2018, match_results)
saveRDS(results, here("Rmd", "sn-assets", "round3-2018", "results_match.rds"))

```

## Round 3 Analysis

We load the model and data:

```{r load-model-data}
model <- stan_model(here("stan", "season_2018.stan"))
init_abilities <- readRDS(here("data", "shrunken_abilities_2018.rds"))
abilities_sd <- readRDS(here("data", "initial_abilities_sd_2018.rds"))
hga_post <- readRDS(here("data", "initial_hga_2018.rds"))
hga_sd <- readRDS(here("data", "initial_hga_sd_2018.rds"))
sigma_y <- readRDS(here("data", "initial_sigma_y_2018.rds"))

```

Now, we need to transform the data into a suitable format for our model. We can use the `superNetballR::matchResults` function for this:

```{r data-munging}
model_data <- season_2018 %>%
    matchResults() %>%
    select(-goals, -squadId, -squadNickname, -squadCode, -points)

```

Next, we need to be able to have the home team, away team, and score difference on a single row for stan:

```{r data-munging-stan}
model_data <- model_data %>%
    group_by(round, game) %>%
    nest() %>%
    group_by(round, game) %>%
    mutate(game_results = map(data, spreadGame)) %>%
    select(-data) %>%
    unnest() %>%
    filter(round <= 2)

```

Now match the data to team ID's and add **Round 3** for predictions:

```{r lookup-table}
teamLookup <- readRDS(here("data", "teamLookup.rds"))
model_data <- left_join(model_data, teamLookup,
                        by = c("homeTeam" = "squadName")) %>%
    rename(homeInt = squadInt, homeColour = squadColour) %>%
    left_join(., teamLookup, by = c("awayTeam" = "squadName")) %>%
    rename(awayInt = squadInt, awayColour = squadColour)
round3_2018 <- data_frame(
    homeSquad = c(4, 7, 3, 5),
    awaySquad = c(6, 8, 1, 2)) %>%
    left_join(., teamLookup, by = c("homeSquad" = "squadInt")) %>%
    rename(homeTeam = squadName,
           homeColour = squadColour) %>%
    left_join(., teamLookup, by = c("awaySquad" = "squadInt")) %>%
    rename(awayTeam = squadName,
           awayColour = squadColour)
saveRDS(round3_2018, here("Rmd", "sn-assets", "round3-2018", "game.rds"))
stan_data <- with(
    model_data, list(nteams = 8, ngames = nrow(model_data),
                     nrounds = max(round), round_no = round, home = homeInt,
                     away = awayInt, score_diff = score_diff,
                     init_ability = init_abilities,
                     init_sd = cbind(abilities_sd[,2], abilities_sd[,3]),
                     mu_hga = hga_post$value,
                     init_sigma_hga = as.numeric(hga_sd),
                     init_sigma_y = as.numeric(sigma_y),
                     ngames_pred = 4,
                     pred_home = round3_2018$homeSquad,
                     pred_away = round3_2018$awaySquad,
                     first_round = 0))

```

Now I can run it:

```{r stan-model,cache=TRUE}
output <- sampling(
    model,
    data = stan_data,
    iter = 2000,
    chains = cores,
    thin = 5,
    open_progress = FALSE,
    control = list(adapt_delta = 0.9,
                   max_treedepth = 10)
)
print(output, digits = 1, pars = c("hga", paste0("a[1,", 1:8, "]")))
print(output, digits = 1, pars = c("pred_ability", "pred_diff", "prob_home"))

```

# Summaries

Now I need to create some summaries. As a highlight, perhaps a histogram of score differences for each game, and the probability of the home team winning.

```{r histogram}
res <- sapply(1:4, predDiffHist, model = output, game_lookup = round3_2018)
## Create a 2x2 grid of the figures.
pl_grid <- plot_grid(res[[1, 1]], res[[1, 2]], res[[1, 3]], res[[1, 4]])
save_plot(here("figs", "round3-2018-plot-grid.png"),
          pl_grid, base_height = 70 / (1 + sqrt(5)), base_width = 35)
## Save prediction table
res_table <- bind_rows(res[2, ]) %>%
    select(
        Home = homeTeam,
        Away = awayTeam,
        `Chance of home team winning` = prob
    )
saveRDS(res_table,
        here("Rmd", "sn-assets", "round3-2018", "predictions.rds"))
for (i in 1:4) {
    ggsave(here("Rmd", "sn-assets", "round3-2018", paste0("game-", i, ".png")),
           res[[1, i]], width = 17.5, height = 35 / (1 + sqrt(5)))
}

```

# Abilities at the end of Round 1

How do the abilities by the end of **Round 1** look?

```{r abilities}
abilities <- extract(output, "a")$a
abilities <- as_data_frame(abilities) %>%
    gather(game, Ability) %>%
    group_by(game) %>%
    summarise(
        ll1 = quantile(Ability, 0.1),
        ll2 = quantile(Ability, 0.25),
        med = quantile(Ability, 0.5),
        ul1 = quantile(Ability, 0.9),
        ul2 = quantile(Ability, 0.75)
    )
ids <- t(sapply(abilities$game, splitRound)) %>%
    as_data_frame() %>%
    unnest()
abilities <- bind_cols(ids, abilities) %>%
    left_join(., teamLookup, by = "squadInt")
sq_cols <- teamLookup$squadColour
names(sq_cols) <- teamLookup$squadName
## Include the initial abilities in
init_ability_df <- teamLookup %>%
    mutate(
        Round = rep(0, 8),
        ll1 = init_abilities,
        ll2 = init_abilities,
        med = init_abilities,
        ul1 = init_abilities,
        ul2 = init_abilities
    )
abilities <- bind_rows(init_ability_df, abilities)
pl_abilities <- ggplot(abilities, aes(x = Round, y = med, group = squadName)) +
    geom_ribbon(aes(ymin = ll1, ymax = ul1, fill = squadName,
                    alpha = 0.05)) +
    geom_ribbon(aes(ymin = ll2, ymax = ul2, fill = squadName,
                    alpha = 0.05)) +
    scale_fill_manual(values = sq_cols, guide = "none") +
    scale_alpha(guide = "none") +
    geom_line(aes(colour = squadName), lwd = 2) +
    scale_colour_manual(values = sq_cols, guide = "none") +
    geom_hline(aes(yintercept = 0), colour = "darkgrey") +
    facet_wrap(~ squadName, nrow = 2) +
    ylab("Ability") +
    xlim(c(0, 14))
ggsave(here("Rmd", "sn-assets", "round3-2018", "abilities.png"),
       pl_abilities, width = 17.5, height = 35 / (1 + sqrt(5)))

```

How do the home ground advantages look?

```{r hga-pred}
hga <- extract(output, "hga")$hga
hga <- as_data_frame(hga)
names(hga) <- teamLookup$squadName
hga <- hga %>%
    gather(squadName, hga) %>%
    group_by(squadName) %>%
    summarise(
        ll1 = quantile(hga, 0.1),
        ll2 = quantile(hga, 0.25),
        med = quantile(hga, 0.5),
        ul1 = quantile(hga, 0.9),
        ul2 = quantile(hga, 0.75)
    )
pl_hga <- ggplot(hga, aes(x = fct_reorder(squadName, med),
                          colour = squadName)) +
    geom_linerange(aes(ymin = ll1, ymax = ul1, alpha = 0.05), lwd = 2) +
    geom_linerange(aes(ymin = ll2, ymax = ul2, alpha = 0.05), lwd = 2.5) +
    geom_point(aes(y = med), size = 4, fill = "white", shape = 21) +
    geom_hline(aes(yintercept = 0), colour = "darkgrey") +
    scale_colour_manual(values = sq_cols, guide = "none") +
    scale_alpha(guide = "none") +
    xlab("Squad") +
    ylab("Home ground advantage") +
    coord_flip()
ggsave(here("Rmd", "sn-assets", "round3-2018", "hga.png"),
       pl_hga, width = 17.5, height = 35 / (1 + sqrt(5)))

```
