---
title: superNetballR Analysis
author:
- Stephen E. Lane
---

<!-- Time-stamp: <2018-04-17 19:48:38 (slane)> -->

```{r setup,echo=FALSE,warning=FALSE,message=FALSE,cache=FALSE,results="hide"}
knitr::opts_chunk$set(cache = FALSE, error = FALSE, warning = FALSE,
                      message = FALSE, echo = TRUE)
options(digits = 2)

```

# Introduction

This document provides notes on setting up my super netball score prediction model using my new `superNetballR` package.

The following packages are required:

```{r libraries}
library(dplyr)
library(tidyr)
library(purrr)
library(superNetballR)
library(rstan)
library(parallel)
library(here)
rstan::rstan_options(auto_write = TRUE)
cores <- round(parallel::detectCores() - 2)
options(mc.cores = cores)

```

We load the model and data:

```{r load-model-data}
model <- stan_model(here("stan", "basic-model.stan"))
data(season_2017)

```

Now, we need to transform the data into a suitable format for our model. We can use the `superNetballR::matchResults` function for this:

```{r data-munging}
model_data <- season_2017 %>%
    matchResults() %>%
    select(-goals, -squadId, -squadNickname, -squadCode, -points)

```

Next, we need to be able to have the home team, away team, and score difference on a single row for stan:

```{r data-munging-stan}
spreadGame <- function(df) {
    home <- df %>%
        filter(isHome == 1) %>%
        rename(homeTeam = squadName) %>%
        select(-isHome)
    away <- df %>%
        filter(isHome == 0) %>%
        rename(awayTeam = squadName) %>%
        select(awayTeam)
    df <- bind_cols(home, away)
    df
}
model_data <- model_data %>%
    group_by(round, game) %>%
    nest() %>%
    group_by(round, game) %>%
    mutate(game_results = map(data, spreadGame)) %>%
    select(-data) %>%
    unnest()

```

Now a lookup table for teams, as that's required for stan as well:

```{r lookup-table}
teamLookup <- data_frame(
    squadName = sort(unique(model_data$homeTeam)),
    squadInt = seq_len(length(squadName))
)
model_data <- left_join(model_data, teamLookup,
                        by = c("homeTeam" = "squadName")) %>%
    rename(homeInt = squadInt) %>%
    left_join(., teamLookup, by = c("awayTeam" = "squadName")) %>%
    rename(awayInt = squadInt)
stan_data <- with(
    model_data, list(nteams = max(homeInt), ngames = nrow(model_data),
                     nrounds = max(round), round_no = round, home = homeInt,
                     away = awayInt, score_diff = score_diff,
                     init_ability = rep(0, max(homeInt)),
                     init_sd = rep(1, max(homeInt)), ngames_pred = 1,
                     pred_home = array(4, 1), pred_away = array(5, 1)))

```

Now I can run it:

```{r stan-model}
output <- sampling(
    model,
    data = stan_data,
    iter = 2000,
    chains = cores,
    open_progress = FALSE,
    control = list(adapt_delta = 0.9,
                   max_treedepth = 10)
)
print(output, digits = 1, pars = c("hga", paste0("a[14,", 1:8, "]")))
print(output, digits = 1, pars = c("pred_ability", "pred_diff", "prob_home"))

```

And there we go, that looks like it works... maybe...

<p>
  <br><br><br>
  All views presented within are the author's only, and do not necessarily represent the views of CEBRA.
  <br><br>
</p>
